### 2021-12-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@925c31f38baa91496e12e982e1cc699c0cb6afe0 🚀

The trained models were then thresholded (again by optimising
informedness), and their predictions transformed back into networks for
analysis; specifically, we measured the connectance, nestedness (REF),
modularity (REF), and entropy (REF). The results are presented in the
following table:

\begin{longtable}[]{@{}lllllllll@{}}
\toprule
Model & MCC & Inf. & ROC-AUC & PR-AUC & Conn. & \(\eta\) & \(Q\) &
Entropy\tabularnewline
\midrule
\endhead
Decision tree & 0.83 & 0.68 & 0.95 & 0.15 & 0.18 & 0.53 & 0.49 &
8.86\tabularnewline
BRT & 0.76 & 0.89 & 0.95 & \textbf{0.65} & 0.22 & 0.63 & 0.43 &
9.14\tabularnewline
Random Forest & \textbf{0.89} & \textbf{0.94} & \textbf{0.99} & 0.41 &
\textbf{0.17} & \textbf{0.48} & \textbf{0.49} &
\textbf{8.80}\tabularnewline
Ridge Regression & 0.67 & 0.85 & 0.89 & 0.38 & 0.27 & 1.0 & 0.26 &
9.40\tabularnewline
Ensemble & 0.84 & 0.91 & \textbf{0.99} & \textbf{0.94} & 0.19 & 0.54 &
0.48 & 8.92\tabularnewline
Data & & & & & 0.16 & 0.45 & 0.49 & 8.71\tabularnewline
\bottomrule
\end{longtable}

>>>>

The trained models were then thresholded (again by optimising
informedness), and their predictions transformed back into networks for
analysis; specifically, we measured the connectance, nestedness (REF),
modularity (REF), and entropy (REF). The results are presented in
tbl.~\ref{tbl:comparison}. The random forest model is an interesting
instance here: it produces the network that looks the most like the
original dataset, despite having a very low PR-AUC, suggesting it hits
high recall at the cost of low precision. Although the ensemble was
about to reach a very high PR-AUC (and a very high ROC-AUC), this did
not necessarilly translate into more accurate reconstructions of the
structure of the network. This result bears elaborating. Measures of
model performance capture how much of the interactions and
non-interactions are correctly identified. As long as these predictions
are not perfect, some interactions will be predicted at the ``wrong''
position in the network; these measures cannot describe the structural
effect of these mistakes. On the other hand, measures of network
structure can have the same value with interactions that fall at
drastically different positions; this is in part because a lot of these
measures covary with connectance, and in part because as long as these
values are not 0 or their respective maximum, there is a large number of
network configurations that can have the same value.

\hypertarget{tbl:comparison}{}
\begin{longtable}[]{@{}lllllllll@{}}
\caption{\label{tbl:comparison}Values of four performance metrics, and
four network structure metrics, for the predictions presented in
fig.~\ref{fig:ecovalid}. The values in \textbf{bold} indicate the best
value for each column (including ties).}\tabularnewline
\toprule
Model & MCC & Inf. & ROC-AUC & PR-AUC & Conn. & \(\eta\) & \(Q\) &
Entropy\tabularnewline
\midrule
\endfirsthead
\toprule
Model & MCC & Inf. & ROC-AUC & PR-AUC & Conn. & \(\eta\) & \(Q\) &
Entropy\tabularnewline
\midrule
\endhead
Decision tree & 0.83 & 0.68 & 0.95 & 0.15 & 0.18 & 0.53 & \textbf{0.49}
& 8.86\tabularnewline
BRT & 0.76 & 0.89 & 0.95 & 0.65 & 0.22 & 0.63 & 0.43 &
9.14\tabularnewline
Random Forest & \textbf{0.89} & \textbf{0.94} & \textbf{0.99} & 0.41 &
\textbf{0.17} & \textbf{0.48} & \textbf{0.49} &
\textbf{8.80}\tabularnewline
Ridge Regression & 0.67 & 0.85 & 0.89 & 0.38 & 0.27 & 1.0 & 0.26 &
9.40\tabularnewline
Ensemble & 0.84 & 0.91 & \textbf{0.99} & \textbf{0.94} & 0.19 & 0.54 &
0.48 & 8.92\tabularnewline
Data & & & & & 0.16 & 0.45 & 0.49 & 8.71\tabularnewline
\bottomrule
\end{longtable}
